---
title: "newscatcheR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{newscatcheR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r preliminaries, echo=FALSE, message=FALSE}
library(newscatcheR)
library(tidyRSS)
```

## Overview

The  package provides three simple functions for reading RSS feeds from news outlets and have them conveniently returned as a tibble.

The _newscatcheR_ package provides a dataset of news sites and their rss feeds, together with some characteristics of the websites such as the topic, country or language of the website, and few functions explore and access the feeds from `R`.

Two functions that work as a wrapper around [tidyRSS](https://github.com/RobertMyles/tidyRSS) can be used to fetch the feed from a given website. Two additional functions can be used to conveniently browse the websites dataset.

### get_news()

The first function `get_news()` returns a tibble of the rss feed of a given site.
```{r, eval = FALSE}
# adding a small time delay to avoid simultaneous posts to the API
Sys.sleep(3)
get_news(website = "ycombinator.com", rss_table = package_rss)
```

### get_headlines()

The second function `get_headlines` is a helper function that returns a tibble of just the headlines, instead of the full rss feed.

```{r, eval = FALSE}
# adding a small time delay to avoid simultaneous posts to the API
Sys.sleep(3)
get_headlines(website = "ycombinator.com", rss_table = package_rss)
```

### describe_url()

Because some website have multiple feeds divided by topics,  `describe_url(website)` can be helpful to see the topics of a given website. 

```{r example_3}
describe_url("bbc.com")
```

### filter_urls()

Finally, `filter_urls(topic, country, language )` can be used to browse the dataset by topic, country, or language.

```{r example_4}
filter_urls(topic = "tech", country = "IT", language = "it")
```

## Use case

This package can be convenient if you need to fetch news from various websites for further analysis and you don't want to search manually for the URL of their RSS feeds.

Assuming we have the news sites we want to follow:

```{r, eval = FALSE}
sites = c("bbc.com", "spiegel.de", "washingtonpost.com")
```

We can get a list of data frames with:

```{r, eval = FALSE}
lapply(sites, get_news)
```
